Dynamic strategies for yaw and induction control of wind farms based on large-eddy simulation and optimization

### 2018-01-02 MuntersMeyers_DynamicStrategiesControl_revision_WM01.tex
R2C6

Two different sets of simulations are considered. The first set is subjected to a steady and uniform inflow with $U_\infty = 8$ m s$^{-1}$. In this case, the top and bottom boundaries are treated with a symmetry condition, and the turbines are placed at the vertical mid-plane $z_h/L_z = 0.5$ to minimize any influence of vertical domain boundaries. The second set applies unsteady turbulent inflow conditions, which are generated in a pressure-driven precursor simulation of an unperturbed turbulent boundary layer with shifted periodic boundary conditions \cite{munters2016shifted}, driven by a pressure gradient of $\partial_x p_\infty/\rho = 2.5 \times 10^{-4}$ m s$^{-2}$, resulting in a freestream wind speed at hub height slightly higher than 8 m s$^{-1}$. In this second case, the top boundary is treated with a stress-free condition, and a high-Reynolds number wall model is used at the bottom. The turbines are placed at a height of $z_h/L_z = 0.1$ from the wall. The wall model adds a wall stress consistent with a rough-wall logarithmic boundary layer profile with roughness length $z_0/L_z = 10^{-4}$, resulting in a inflow turbulence intensity of about 8\% at hub height.

>>>>

Two different sets of simulations are considered. The first set is subjected to a steady and uniform inflow with $U_\infty = 8$ m s$^{-1}$. In this case, the top and bottom boundaries are treated with a symmetry condition, \revision{and the vertical location of the turbine hubs $z_h$ is placed at the vertical mid-plane of the domain, i.e. $z_h/L_z = 0.5$,} in order to minimize any influence of vertical domain boundaries. The second set applies unsteady turbulent inflow conditions, which are generated in a pressure-driven precursor simulation of an unperturbed turbulent boundary layer with shifted periodic boundary conditions \cite{munters2016shifted}, driven by a pressure gradient of $\partial_x p_\infty/\rho = 2.5 \times 10^{-4}$ m s$^{-2}$, resulting in a freestream wind speed at hub height slightly higher than 8 m s$^{-1}$. In this second case, the top boundary is treated with a stress-free condition, and a high-Reynolds number wall model is used at the bottom. The turbines are placed at a height of $z_h/L_z = 0.1$ from the wall. The wall model adds a wall stress consistent with a rough-wall logarithmic boundary layer profile with roughness length $z_0/L_z = 10^{-4}$, resulting in a inflow turbulence intensity of about 8\% at hub height.
